\section{Results}
\subsection{Raw results}
The experts have sent us their evaluations in various formats. We wanted every problem in the following format:
\begin{enumerate}
    \item Problem description
    \item Difficulties
    \item Specific contexts
    \item Assumed causes
\end{enumerate}
This is the format from Cockton, Woolrych, Hall, Hindmarch, 2003\cite{woolrych2003changing}

Unfortunately, only 3 out of 6 experts followed this exact format. We blame this on bad communication from our side, since we only mentioned this over WhatsApp. In the future, we'd likely at a preface to our prototype explaining what we format we want so it's less likely someone reads over it. Having a template for the experts to fill in and/or an example could also have helped.


\subsection{Results summarized}
We grouped the problem into 2 categories. Problems with features and problems with design. If multiple people found the same problem, we added a counter to the issue (e.g. (3x) )

\subsubsection{Feature problems}
\begin{itemize}
    \item You can't disconnect from the server (3x)
    \item No way for the admin to sign in
    \item You can't edit the board name
    \item There isn't an error dialog for connecting to the server - you should distinguish between a malfunction and a mistake
    \item Edit card should have the option to change the description
\end{itemize}

\subsubsection{Design problems}
By aggregating the raw reports, we've come up with the following problems:
\begin{itemize}
    \item 4 - It's unclear if you can drag items between lists (3x).
    \item 6 - it's unclear that the edit button is for the whole card and not only the title
    \item 6 - Add list button shouldn't be in the same box as the board name
    \item Bad visual hierarchy in board overview
    \item 8 - Board overview doesn't have enough contrast, there should be more different colors (2x)
    \item 5 - The user should be warned if they add a card or list with the same name as an already existing one.
    \item 5 - Color schema doesn't work (delete button doesn't go well with background)
    \item 8 - Three buttons on top of the popup are confusing to edit cards are confusing since there are already buttons on the bottom.
    \item 4 - There shouldn't be scrollbars if you can't scroll down (i.e. everything is in view)
    \item 4 - Buttons don't all follow the same format so users might be confused about whether something is a button. (some are grey, some green)
    \item 4 - Titles don't follow conventions,
    they should be bigger than other text and centered.
    \item 4- Unrelated buttons shouldn't be grouped together. Right now add card and edit list are next to each other. This is confusing.
    \item 1 - When adding a card or list, it isn't clear what happens if you don't fill in a title. It should either be pre-filled with something like 'untitled' or the apply button should be impossible to click before inputting something.
    \item 8 - editing inputs are too small
\end{itemize}
